Design and Implementation of\\Anglican Probabilistic Programming Language

### 2016-09-01 slides/slides.tex
drafted, pause

\section{Definitions and Runtime Library}

>>>>

\begin{frame}[fragile]{Importance sampling}

Importance sampling is the simplest:
\begin{minted}[linenos, fontsize=\small]{clojure}
(defmethod infer :importance [_ prog value & {}]
  (letfn
    [(sample-seq []
       (lazy-seq
         (cons
           (:state (exec ::algorithm prog value
                         initial-state))
           (sample-seq))))]
    (sample-seq)))
\end{minted}
Default checkpoint handlers are called:
\begin{minted}[linenos, fontsize=\scriptsize]{clojure}
(defmethod checkpoint [::algorithm anglican.trap.observe] [_ obs]
  #((:cont obs) nil (add-log-weight (:state obs)
                                    (observe* (:dist obs) (:value obs)))))

(defmethod checkpoint [::algorithm anglican.trap.sample] [_ smp]
  #((:cont smp) (sample* (:dist smp)) (:state smp)))
\end{minted}
\end{frame}

\begin{frame}{Other inference algorithms}
    \begin{itemize}
        \item Implement \texttt{infer}.
        \item Redefine one or both checkpoints.
        \item An average implementation is $\approx 150$ lines of source
            code.
        \item A dozen different inference algorithms are in the
            code base.
        \item Half of them are really useful.
    \end{itemize}
\end{frame}

\begin{frame}{Recap}
    \begin{itemize}
        \item Anglican is integrated with Clojure.
        \item Shares syntax but alters semantics.
        \item Macro-compiled.
        \item Efficient.
        \item Makes implementing AND using inference easy.
    \end{itemize}
\end{frame}
